\documentclass[letterpaper,9pt]{article}

% ============================================
% PACKAGES
% ============================================
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{tikz}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{montserrat}  % Google Product Sans alternative
\usepackage{opensans}    % Clean body font
\usepackage{graphicx}

\usetikzlibrary{shapes.geometric, shadows.blur, calc}

% ============================================
% GEOMETRY
% ============================================
\geometry{
    left=0.5in,
    right=0.4in,
    top=0.28in,
    bottom=0.2in
}

% Google Colors
\definecolor{GoogleBlue}{HTML}{4285F4}
\definecolor{GoogleRed}{HTML}{EA4335}
\definecolor{GoogleYellow}{HTML}{FBBC05}
\definecolor{GoogleGreen}{HTML}{34A853}
\definecolor{GoogleGray}{HTML}{5F6368}
\definecolor{GoogleLightGray}{HTML}{DADCE0}
\definecolor{LinkBlue}{HTML}{1A0DAB}
\definecolor{UrlGreen}{HTML}{1E8E3E}
\definecolor{TextBlack}{HTML}{202124}
\definecolor{SubtleGray}{HTML}{70757A}
\definecolor{PanelBorder}{HTML}{DFE1E5}
\definecolor{AIOverviewBg}{HTML}{F0F4F9}
\definecolor{AIOverviewBorder}{HTML}{C2E7FF}
\definecolor{AIPurple}{HTML}{7B61FF}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Use Open Sans for body text
\renewcommand{\familydefault}{\sfdefault}

% ============================================
% CUSTOM COMMANDS
% ============================================

% Google Logo - Using Montserrat Bold (closest to Product Sans)
\newcommand{\GoogleLogoSmall}{%
    \begingroup
    \fontfamily{Montserrat-TOsF}\selectfont
    \fontsize{20}{22}\selectfont\bfseries%
    {\color{GoogleBlue}G}%
    {\color{GoogleRed}o}%
    {\color{GoogleYellow}o}%
    {\color{GoogleBlue}g}%
    {\color{GoogleGreen}l}%
    {\color{GoogleRed}e}%
    \endgroup
}

% ============================================
% DOCUMENT
% ============================================
\begin{document}

% ============================================
% HEADER
% ============================================
\begin{tabular}{@{}l@{\hspace{14pt}}l@{}}
\GoogleLogoSmall &
\begin{tikzpicture}[baseline=-3pt]
    \node[
        draw=GoogleLightGray,
        rounded corners=18pt,
        minimum height=30pt,
        text width=4.4in,
        inner xsep=10pt,
        inner ysep=0pt,
        fill=white,
        line width=0.6pt
    ] {%
        {\small\color{GoogleGray}\faSearch}~~%
        {\fontfamily{fos}\selectfont\small Ayush Singh - Distributed Systems Jedi}%
        \hfill%
        {\small\color{GoogleGray}\faTimes}~~%
        {\small\color{GoogleBlue}\faMicrophone}%
    };
\end{tikzpicture}
\end{tabular}

\vspace{5pt}

% Navigation Bar with contact links
{\fontfamily{fos}\selectfont\footnotesize\color{SubtleGray}%
{\color{GoogleBlue}\underline{All}}%
\hspace{14pt}%
\href{https://linkedin.com/in/iu-sh}{{\color{SubtleGray}\faLinkedin}~LinkedIn}%
\hspace{14pt}%
\href{https://github.com/WinterSoldier13}{{\color{SubtleGray}\faGithub}~GitHub}%
\hspace{14pt}%
\href{https://ayushsingh.is-a.dev}{{\color{SubtleGray}\faGlobe}~Website}%
\hspace{14pt}%
\href{mailto:ayushsingh1315@gmail.com}{{\color{SubtleGray}\faEnvelope}~Email}%
}

\vspace{2pt}
{\color{GoogleLightGray}\hrule height 0.4pt}
\vspace{6pt}

% ============================================
% MAIN CONTENT - TWO COLUMNS
% ============================================
\begin{minipage}[t]{0.58\textwidth}

% AI Overview Section (new Google style)
\begin{tikzpicture}
\node[
    fill=AIOverviewBg,
    draw=AIOverviewBorder,
    rounded corners=12pt,
    inner sep=8pt,
    text width=0.95\linewidth,
    line width=0.5pt
] {%
    {\color{AIPurple}\faRobot}~~{\fontfamily{Montserrat-TOsF}\selectfont\small\bfseries\color{TextBlack}AI Overview}\\[4pt]
    {\fontfamily{fos}\selectfont\footnotesize\color{TextBlack}%
    \textbf{TL;DR: Swiss Army Knife} -- Versatile engineer specializing in Privacy \& Compliance, Distributed Systems, and Full-Stack Development. Currently at Google Munich building consent systems that protect user data across all Google products. Led UK's Online Safety Act implementation. \textbf{Promoted within 1.2 years} for significant impact. Awarded \textbf{spot bonus from VP of Engineering}.%
    }%
};
\end{tikzpicture}

\vspace{6pt}

% Experience Section
{\fontfamily{Montserrat-TOsF}\selectfont\normalsize\bfseries\color{TextBlack}Experience}
\vspace{4pt}

% Google Munich
{\fontfamily{fos}\selectfont%
{\footnotesize\color{UrlGreen}careers.google.com › munich › swe-iii}\\[-2pt]
{\color{LinkBlue}\bfseries Software Engineer III} · Google, Munich\\[1pt]
{\footnotesize\color{SubtleGray}November 2024 -- Present}\\[2pt]
{\footnotesize\color{TextBlack}%
\textbullet~Working in SignedOut Consent team, managing user data privacy across all Google Products.\\[0pt]
\textbullet~Led \textbf{UK's Online Safety Act} implementation across web, Android, iOS. \textbf{Spot bonus from VP}.\\[0pt]
\textbullet~Drove US AppStore Age Verification---saving Google from millions in fines.\\[0pt]
\textbullet~Revamped backend for privacy signals, significantly simplifying infrastructure.%
}%
}

\vspace{5pt}

% Google India
{\fontfamily{fos}\selectfont%
{\footnotesize\color{UrlGreen}careers.google.com › india › swe-iii}\\[-2pt]
{\color{LinkBlue}\bfseries Software Engineer III} · Google, India\\[1pt]
{\footnotesize\color{SubtleGray}July 2022 -- November 2024}\\[2pt]
{\footnotesize\color{TextBlack}%
\textbullet~Built BinaryFileSystem---scalable file system for critical binary assets deployment.\\[0pt]
\textbullet~Led Chrome's cookie deprecation impact tool. \textbf{CEO's go-ahead}. \textbf{Promoted in 1.2 years}.\\[0pt]
\textbullet~SLA/SLO enforcement system, saving Google \textbf{\$2.5M/quarter}.\\[0pt]
\textbullet~Telemetry extraction from distributed systems; highly available aggregation backend.\\[0pt]
\textbullet~Co-authored 3 Technical Design Documents.%
}%
}

\vspace{5pt}

% Komprise
{\fontfamily{fos}\selectfont%
{\footnotesize\color{UrlGreen}komprise.com › careers}\\[-2pt]
{\color{LinkBlue}\bfseries Software Engineer Intern} · Komprise~{\footnotesize\color{SubtleGray}| Jan -- Jun 2022}\\[1pt]
{\footnotesize\color{TextBlack}%
Automation Engine for parallelizing operations. BVT suite optimization---\textbf{87.5\% faster}.%
}%
}

\vspace{4pt}

% Accenture
{\fontfamily{fos}\selectfont%
{\footnotesize\color{UrlGreen}accenture.com › careers}\\[-2pt]
{\color{LinkBlue}\bfseries Data Engineer Intern} · Accenture~{\footnotesize\color{SubtleGray}| May -- Jul 2021}\\[1pt]
{\footnotesize\color{TextBlack}%
BI Dashboard with AWS S3 → Snowflake pipeline. NLP chatbot for data insights.%
}%
}

\vspace{4pt}

% Tookitaki
{\fontfamily{fos}\selectfont%
{\footnotesize\color{UrlGreen}tookitaki.com › careers}\\[-2pt]
{\color{LinkBlue}\bfseries Software Engineer Intern} · Tookitaki, Singapore~{\footnotesize\color{SubtleGray}| Oct 2020 -- Jan 2021}\\[1pt]
{\footnotesize\color{TextBlack}%
Spark Structured-Streaming + ActiveMQ. Reduced latency \textbf{0.85s → <0.05s}.%
}%
}

\vspace{6pt}

% People also ask - Projects
{\fontfamily{Montserrat-TOsF}\selectfont\normalsize\bfseries\color{TextBlack}People also ask about my projects}~~{\footnotesize\color{SubtleGray}:}
\vspace{3pt}

{\fontfamily{fos}\selectfont%
\fbox{\parbox{0.94\linewidth}{\vspace{2pt}{\footnotesize\color{TextBlack}\bfseries \href{https://github.com/iu-sh/ytm_ai_host}{What is YTM AI Host?}}\hfill{\color{GoogleGray}\scriptsize\faChevronDown}\\[-2pt]{\scriptsize\color{SubtleGray} AI Radio Jockey for YouTube Music. Uses Gemini API + WebLLM for text generation. Multiple TTS engines (Chrome TTS, Kokoro JS, XTTS v2). Smart caching \& pre-fetching for seamless playback.}\vspace{2pt}}}\\[2pt]
\fbox{\parbox{0.94\linewidth}{\vspace{2pt}{\footnotesize\color{TextBlack}\bfseries \href{https://youtu.be/0Fff2ncdbPo}{What is Pika Autonomous Robot?}}\hfill{\color{GoogleGray}\scriptsize\faChevronDown}\\[-2pt]{\scriptsize\color{SubtleGray} Autonomous robot using Computer Vision for navigation. TensorFlow + OpenCV on Raspberry Pi. Processes sensor data on-board for real-time decision making.}\vspace{2pt}}}\\[2pt]
\fbox{\parbox{0.94\linewidth}{\vspace{2pt}{\footnotesize\color{TextBlack}\bfseries \href{https://github.com/WinterSoldier13/linkinJMS}{What is LinkinJMS?}}\hfill{\color{GoogleGray}\scriptsize\faChevronDown}\\[-2pt]{\scriptsize\color{SubtleGray} Low-latency ActiveMQ connector built from scratch. Spark + Scala. <0.05s latency with enhanced AMQP security. Supports read/write to topics \& queues.}\vspace{2pt}}}\\[2pt]
\fbox{\parbox{0.94\linewidth}{\vspace{2pt}{\footnotesize\color{TextBlack}\bfseries \href{https://github.com/WinterSoldier13/professorMirror}{What is Professor-Mirror?}}\hfill{\color{GoogleGray}\scriptsize\faChevronDown}\\[-2pt]{\scriptsize\color{SubtleGray} Professor rating platform. Node.js + Firebase + MongoDB. Rate professors on Research, Course Material, Student Interaction.}\vspace{2pt}}}%
}

\end{minipage}%
\hfill%
% ============================================
% RIGHT COLUMN - KNOWLEDGE PANEL
% ============================================
\begin{minipage}[t]{0.38\textwidth}

\fboxsep=7pt
\fboxrule=0.5pt
\fcolorbox{PanelBorder}{white}{%
\begin{minipage}[t]{0.88\linewidth}

{\fontfamily{Montserrat-TOsF}\selectfont\Large\bfseries\color{TextBlack}Ayush Singh}\\[1pt]
{\fontfamily{fos}\selectfont\small\color{SubtleGray}Software Engineer - III @ Google, Munich}

\vspace{4pt}
{\color{GoogleLightGray}\rule{\linewidth}{0.3pt}}
\vspace{4pt}

{\fontfamily{Montserrat-TOsF}\selectfont\small\bfseries\color{TextBlack}About}\\[2pt]
{\fontfamily{fos}\selectfont\scriptsize\color{TextBlack}%
Software Engineer at Google Munich specializing in privacy systems and distributed architecture. Expert in full-stack development.%
}

\vspace{4pt}

{\fontfamily{fos}\selectfont\scriptsize%
\textbf{\color{SubtleGray}Location:}~{\color{TextBlack}Munich, Germany}\\[1pt]
\textbf{\color{SubtleGray}Experience:}~{\color{TextBlack}4+ years}\\[1pt]
\textbf{\color{SubtleGray}Current:}~{\color{TextBlack}SWE III @ Google}\\[1pt]
\textbf{\color{SubtleGray}Education:}~{\color{LinkBlue}\href{https://www.nita.ac.in/}{NIT Agartala}}\\[1pt]
\textbf{\color{SubtleGray}Degree:}~{\color{TextBlack}B.Tech (EE)}\\[1pt]
\textbf{\color{SubtleGray}CGPA:}~{\color{TextBlack}9.32/10}%
}

\vspace{4pt}
{\color{GoogleLightGray}\rule{\linewidth}{0.3pt}}
\vspace{4pt}

{\fontfamily{Montserrat-TOsF}\selectfont\small\bfseries\color{TextBlack}Contact}\\[2pt]
{\fontfamily{fos}\selectfont\scriptsize%
\faPhone*~{\color{TextBlack}+91-7766942620}\\[1pt]
\faEnvelope~{\color{LinkBlue}\href{mailto:ayushsingh1315@gmail.com}{ayushsingh1315@gmail.com}}\\[1pt]
\faLinkedin~{\color{LinkBlue}\href{https://linkedin.com/in/iu-sh}{linkedin.com/in/iu-sh}}\\[1pt]
\faGlobe~{\color{LinkBlue}\href{https://ayushsingh.is-a.dev}{ayushsingh.is-a.dev}}%
}

\vspace{4pt}
{\color{GoogleLightGray}\rule{\linewidth}{0.3pt}}
\vspace{4pt}

{\fontfamily{Montserrat-TOsF}\selectfont\small\bfseries\color{TextBlack}Skills}\\[2pt]
{\fontfamily{fos}\selectfont\scriptsize\color{TextBlack}%
TypeScript · C++ · Java · Scala · Python · Kotlin · Spark · Kafka · React · Node.js · Docker · TensorFlow · PyTorch%
}

\vspace{4pt}
{\color{GoogleLightGray}\rule{\linewidth}{0.3pt}}
\vspace{4pt}

{\fontfamily{Montserrat-TOsF}\selectfont\small\bfseries\color{TextBlack}Achievements}\\[2pt]
{\fontfamily{fos}\selectfont\scriptsize\color{TextBlack}%
{\color{GoogleBlue}\faTrophy}~7 Peer Bonuses at Google\\[0pt]
{\color{GoogleBlue}\faTrophy}~3 Spot Bonuses at Google\\[0pt]
{\color{GoogleGreen}\faMedal}~Rank 1 GFG at NIT-A\\[0pt]
{\color{GoogleRed}\faGraduationCap}~1 of 50: Google ExploreML\\[0pt]
{\color{GoogleBlue}\faAward}~IAS Fellowship 2021 (1/11)\\[0pt]
{\color{GoogleGreen}\faUsers}~Founded DSC @ NIT-A%
}

\end{minipage}%
}

\vspace{4pt}

% Profiles
\fcolorbox{PanelBorder}{white}{%
\begin{minipage}[t]{0.88\linewidth}
\vspace{3pt}
{\fontfamily{Montserrat-TOsF}\selectfont\small\bfseries\color{TextBlack}Profiles}\\[3pt]
{\fontfamily{fos}\selectfont\scriptsize%
{\color{GoogleBlue}\faLinkedin}~{\color{LinkBlue}\href{https://linkedin.com/in/iu-sh}{LinkedIn}}%
\hspace{6pt}%
{\color{TextBlack}\faGithub}~{\color{LinkBlue}\href{https://github.com/WinterSoldier13}{GitHub}}%
\hspace{6pt}%
{\color{GoogleBlue}\faGlobe}~{\color{LinkBlue}\href{https://ayushsingh.is-a.dev}{Portfolio}}%
}
\vspace{3pt}
\end{minipage}%
}

\vspace{4pt}

% Related searches
{\fontfamily{fos}\selectfont\scriptsize\color{SubtleGray}Related searches}\\[2pt]
{\fontfamily{fos}\selectfont\scriptsize%
{\color{GoogleGray}\faSearch}~{\color{LinkBlue}\href{https://www.google.com/search?q=ayush+singh+google+engineer}{ayush singh google engineer}}\\[0pt]
{\color{GoogleGray}\faSearch}~{\color{LinkBlue}\href{https://github.com/WinterSoldier13}{ayush singh github projects}}\\[0pt]
{\color{GoogleGray}\faSearch}~{\color{LinkBlue}\href{https://ayushsingh.is-a.dev}{ayush singh portfolio}}%
}

\end{minipage}

\end{document}
